{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to Near-Infrared Spectroscopy}

### 2022-01-16 Presentation/slides.tex
Additional Aux Slide

	\begin{frame}{Estimation via Basis Representation}
		We can transform the data generating process into:
		\begin{equation}\notag
			\begin{split}
				Y(\omega) & = \alpha + \int_{0}^{1}\left[\left(\sum_{j \in \mathcal{I}} c_j  \phi_j(s)\right) X(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
						  & = \alpha + \sum_{j \in \mathcal{I}} \left[c_j \textcolor{red}{\int_{0}^{1} X(\omega)(s) \phi_j(s)\mathrm{d}s}\right] + \epsilon(\omega)	 \\
						  & = \alpha + \sum_{j \in \mathcal{I}} c_j {\color{red}Z_j(\omega)} + \epsilon(\omega)  \approx  \alpha + \sum_{j = 1}^{L} c_j {\color{red}Z_j(\omega)}  + \epsilon(\omega)
			\end{split}
		\end{equation}

		Where a $Z_j(\omega)$ is a \textbf{scalar random variable}.
	\end{frame}

@@

		This is dependent on...\vspace{-0.2cm}
		\begin{multicols}{2}
			\begin{itemize}
				\item The basis $(\phi_j(t))_{j \in \mathcal{I}}$ for the estimation of $\beta(t)$
				\item The truncation parameter $L$\vfill\null
				\item The basis $(\psi_j(t))_{j \in \mathcal{L}}$ used for the observations
				\item The truncation parameter for the observations $K$
			\end{itemize}
		\end{multicols}

@@

>>>>

	\begin{frame}{Estimation via Basis Representation}\label{ReducedEq}
		We can transform the data generating process into:
		\begin{equation}\notag
			\begin{split}
				Y(\omega) & = \alpha + \int_{0}^{1}\left[\left(\sum_{j \in \mathcal{I}} c_j  \phi_j(s)\right) X(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
						  & = \alpha + \sum_{j \in \mathcal{I}} \left[c_j \textcolor{red}{\int_{0}^{1} X(\omega)(s) \phi_j(s)\mathrm{d}s}\right] + \epsilon(\omega)	 \\
						  & = \alpha + \sum_{j \in \mathcal{I}} c_j {\color{red}Z_j(\omega)} + \epsilon(\omega)  \approx  \alpha + \sum_{j = 1}^{L} c_j {\color{red}Z_j(\omega)}  + \epsilon(\omega)
			\end{split}
		\end{equation}

		Where a $Z_j(\omega)$ is a \textbf{scalar random variable}.

		\hyperlink{FullEq}{\beamergotobutton{Equation with Approximated Functions}}
	\end{frame}

@@

		This is dependent on...\vspace{-0.2cm}
		\begin{multicols}{2}
			\begin{itemize}
				\item The basis $(\phi_j(t))_{j \in \mathcal{I}}$ for the estimation of $\beta(t)$
				\item The truncation parameter $L$\vfill\null
				\item The basis $(\psi_j(t))_{j \in \mathcal{L}}$ used for the observations
				\item The truncation parameter for the observations $K$
			\end{itemize}
		\end{multicols}
	\end{frame}

@@

	\begin{frame}{Estimation with Approximated Functions}\label{FullEq}
		{\small
		\begin{equation}\notag
			\begin{split}
				Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega) \\
				& = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
				& = \alpha + \sum_{j \in \mathcal{I}} \left[ c_j \sum_{k \in \mathcal{L}} \textcolor{teal}{d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s}\right] + \epsilon(\omega) \\
				& = \alpha + \sum_{j \in \mathcal{I}} \left[c_j \sum_{k \in \mathcal{L}}  \textcolor{teal}{Z_{j, k}(\omega)} \right] + \epsilon(\omega) \\
				& \approx \alpha + \sum_{j = 1}^{L} \left[c_j \textcolor{violet}{\sum_{k = 1}^{K}  Z_{j, k}(\omega)} \right] + \epsilon(\omega)
				= \alpha + \sum_{j = 1}^{L} \left[c_j \textcolor{violet}{\tilde{Z}_{j}^{K}(\omega)} \right] + \epsilon(\omega)	
			\end{split}
		\end{equation}}
		\hyperlink{ReducedEq}{\beamergotobutton{Equation without Approximated Functions}}
	\end{frame}

### 2022-01-16 main.tex
Correction
Additional Aux Slide

	\begin{equation}
			Y(\omega) \approx \alpha + \sum_{j = 1}^{L} \psi_j Z_j(\omega) + \epsilon(\omega)
	\end{equation}

@@

	\begin{equation}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j \in \mathcal{I}} \left[ c_j \sum_{k \in \mathcal{L}} \textcolor{teal}{d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s}\right] + \epsilon(\omega)
			= \alpha + \sum_{j \in \mathcal{I}} \left[c_j \sum_{k \in \mathcal{L}}  \textcolor{teal}{Z_{j, k}(\omega)} \right] + \epsilon(\omega) \\
			& \approx \alpha + \sum_{j = 1}^{J} \left[c_j \textcolor{violet}{\sum_{k = 1}^{K}  Z_{j, k}(\omega)} \right] + \epsilon(\omega)
			= \alpha + \sum_{j = 1}^{J} \left[c_j \textcolor{violet}{\tilde{Z}_{j}(\omega)} \right] + \epsilon(\omega)	
		\end{split}
	\end{equation}

>>>>

	\begin{equation}
			Y(\omega) \approx \alpha + \sum_{j = 1}^{L} c_j Z_j(\omega) + \epsilon(\omega)
	\end{equation}

@@

	\begin{equation}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j \in \mathcal{I}} \left[ c_j \sum_{k \in \mathcal{L}} \textcolor{teal}{d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s}\right] + \epsilon(\omega)
			= \alpha + \sum_{j \in \mathcal{I}} \left[c_j \sum_{k \in \mathcal{L}}  \textcolor{teal}{Z_{j, k}(\omega)} \right] + \epsilon(\omega) \\
			& \approx \alpha + \sum_{j = 1}^{J} \left[c_j \textcolor{violet}{\sum_{k = 1}^{K}  Z_{j, k}(\omega)} \right] + \epsilon(\omega)
			= \alpha + \sum_{j = 1}^{J} \left[c_j \textcolor{violet}{\tilde{Z}_{j}^{K}(\omega)} \right] + \epsilon(\omega)	
		\end{split}
	\end{equation}
